Predicting sales of newly published books

### 2015-11-03 paper.tex
Little grammar error and comment

In general, historical data is used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns 
is difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data is available in this problem).

>>>>

In general, historical data is used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns 
are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data is available in this problem).
% (Paloma) - Se deberían evitar paréntetis.
